Low-lying collective excited states in non-integrable system based on stationary phase approximation to the path integral

### 2018-09-14 paper2/draft1-1.tex
draft1.1

With the properties of the constant of motion, we discuss the practical solution of ASCC in pairing model. If we ignore the higher order term $f^{(1)1\alpha\beta}$, we can practice local harmonic equation (LHE)
\begin{align}
  B^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
  B^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1},
  \label{LHE}
\end{align}
which simplifies the moving-frame QRPA equation (\ref{mfQRPA}) by replacing $\tilde{B}^{\beta\gamma}$ into $B^{\beta\gamma}$. Under (\ref{LHE}), the eigenvalue of spurious mode corresponding pairing rotation is exact zero. Moreover, we can skip the Step. 4 in Sec. \ref{ASCC}. After obtain the energy minimum point by solving normal HFB equation, we only use (\ref{LHE}) one after another to construct the one-dimensional collective Hamiltonian without moving-frame HFB equation (\ref{mfHFB}). It arises the uncertainty of the total gauge angle $\Phi$ during obtaining the collective path. To arrange the eigenvectors with $\Phi(q)=-\frac{1}{L} p_1\sum_l f^1_{,l}=0$, we correct the eigenvectors by
\begin{align}
  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_l f^1_{,l} 
  \label{f}
\end{align}
after solving (\ref{LHE}) at each point of $q$.

@@

\subsection{Three-level system}
The simplest non-integrable system is three-level system. We have one trivial motion and two time-dependent degrees of freedom. We study the system with $\Omega_1=\Omega_2=\Omega_3=8$, $\epsilon_1=-1$, $\epsilon_2=0$, $\epsilon_3=1.5$, and $g=0.2$.

>>>>

With the properties of the constant of motion, we discuss the practical solution of ASCC in pairing model. If we ignore the higher order term $f^{(1)1\alpha\beta}$, we can practice local harmonic equation (LHE)
\begin{align}
  B^{\beta\gamma}V_{;\gamma\alpha}f^1_{,\beta}  &= \omega^2 f^1_{,\alpha},\hspace{2em} 
  B^{\beta\gamma}V_{;\gamma\alpha}g^{\alpha}_{,1} = \omega^2 g^{\beta}_{,1},
  \label{LHE}
\end{align}
which simplifies the moving-frame QRPA equation (\ref{mfQRPA}) by replacing $\tilde{B}^{\beta\gamma}$ into $B^{\beta\gamma}$. Under (\ref{LHE}), the eigenvalue of spurious mode corresponding pairing rotation is exact zero. To guarantee the state vectors $\ket{Z(q)}$ are in the same total gauge angle $\Phi(q)=-\frac{1}{L} p_1\sum_l f^1_{,l}=0$, we correct the eigenvectors by
\begin{align}
  f^1_{,\alpha} \to f^1_{,\alpha} - \frac{1}{L}\sum_l f^1_{,l} 
  \label{f}
\end{align}
after solving (\ref{LHE}) at each point of $q$.

@@

\subsection{Three-level system}
The simplest non-integrable system is three-level system. We have one trivial motion and two time-dependent degrees of freedom. We study the system with $\Omega_1=\Omega_2=\Omega_3=8$, $\epsilon_1=-1$, $\epsilon_2=0$, $\epsilon_3=1.5$, and $g=0.2$. The phase transition occurs at $g_c=0.058$ when $N=2\Omega_1=16$. We consider the even particle number chain from $N=14$ to $N=24$.

The pairing correlation is strong enough for low-lying $0^+$ states to have closed TDHFB trajectories.

\begin{figure*}[t]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{potential.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{fig:N8Pad}
\end{figure*}
\begin{figure*}[t]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{omega_sq.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{fig:N8Pad}
\end{figure*}
\begin{figure*}[t]
 \begin{center}
  \includegraphics[width=40mm,angle=-90]{occ_number.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{fig:N8Pad}
\end{figure*}

\begin{table}
\begin{ruledtabular}
\begin{tabular}{c|c|cccccc}
            & $N$ & $14$ & $16$ & $18$ & $20$ & $22$ & $24$\\ \hline
$0_2^+$ & Exact & $4.09$ & $4.13$ & $4.20$ & $4.30$ & $4.44$ & $4.60$\\
&ASCC+SPA & $3.87$ & $3.90$ & $3.97$ & $4.09$ & $4.23$ & $4.33$\\ \hline
$0_4^+$& Exact & $7.65$ & $7.71$ & $7.88$ & $8.15$ & $8.49$ & $8.74$\\
&ASCC+SPA & $7.42$ & $7.42$ & $7.60$ & $7.94$ & $8.26$ & $8.47$\\
\end{tabular}
\end{ruledtabular}
\caption{\label{ex}Excitation energy.}
\end{table}

\begin{figure}[t]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{intra_trans.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{3levelPad}
\end{figure}

\begin{figure}[t]
 \begin{center}
  \includegraphics[width=60mm,angle=-90]{inter_trans.eps}
 \end{center}
 \captionsetup{labelformat=empty,labelsep=none}
	\caption{aa.
}
 \label{3levelPad}
\end{figure}
